\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer (Back-End) Part-Time} % Job title
    {Advotics} % Organization
    {South Jakarta} % Location
    {Dec. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advotics is a Supply Chain SaaS startup, focusing on digitalizing supply chain activities, with numerous clients.
        \item Part of \textbf{Distribution Team}, implemented new feature and reviewed codes on Purchase Order, Sales Order, Sales Return module.
        \item Implemented message queue module using Apache Kafka on Advotics' source code.
      \end{cvitems}
    }
    
  \cventry
    {Research Assistant} % Job title
    {Universitas Indonesia} % Organization
    {Depok, West Java} % Location
    {May. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Helped Mrs. Erdefi Rakun's research by implementing \textbf{SIBI (Sistem Isyarat Bahasa Indonesia)} mobile app using Kotlin to detect hand motion and translating into text.
      \end{cvitems}
    }

  \cventry
    {Software Engineer (Full-Stack) Intern} % Job title
    {Advotics} % Organization
    {South Jakarta} % Location
    {May 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Built \textbf{Track and Trace} module, to be used widely on Advotics' source code and referenced by other modules entirely, started from database designing, core logics, ETL and data warehousing design.
        \item Designed database tables to be injected by hundred thousands of datas monthly, supervised directly by the CTO.
        \item Fixed forgot password logic and flows on Advotics' storefront mobile app.
      \end{cvitems}
    }
    
  \cventry
    {Head of Mobile Application Development Special Interest Group (SIG)} % Job title
    {RISTEK Fasilkom UI} % Organization
    {Depok, West Java} % Location
    {Jan. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item First RISTEK Fasilkom UI's Mobile Application Development Head to implement \textbf{Flutter} as its main learning stack.
        \item Courses covered: Dart Language, Widgets, BLoC Design Pattern, API Communication
        \item Delivered 1 external project throughout the year.
      \end{cvitems}
    }
    
  \cventry
    {Teaching Assistant}
    {Universitas Indonesia}
    {Depok, West Java}
    {Aug. 2018 - Jun. 2019}
    {
      \begin{cvitems}
        \item \textbf{Web Design and Programming} - Attended lab sessions, assisted lecturer in-class session, graded assignments, conducted code demos, checked students' final project deployment.
        \item \textbf{Database} - Attended lab sessions, assisted lecturer in-class session, graded assignments, conducted database design and code demos, checked students' final project deployment.
      \end{cvitems}
    }
    
  \cventry
    {Lead Android/iOS Developer}
    {adaTeman}
    {Depok, West Java}
    {Jun. 2018 - Apr. 2019}
    {
      \begin{cvitems}
        \item adaTeman is a social media lending platform, where users can lend and/or borrow things for free and given vouchers in return that can be redeemed with meals in local food stalls and restaurants.
        \item Contributed in product design and concept, evaluated users' experiences.
        \item Led the early stage of development, created code conventions and utilities using Flutter.
      \end{cvitems}
    }
\end{cventries}
