\cvsection{Projects}

\begin{cventries}
  \cventry
    {Backend Developer} % Empty position
    {Portal Informasi Desa (PADE)} % Project
    {Institut Teknologi Bandung} % Empty location
    {February 2020} % Empty date
    {
      \begin{cvitems} % Description(+s) bullet points
        \item Submission for \textbf{Arkavidia 6.0} Institut Teknologi Bandung Hackathon Contest (Hackavidia) Final Round.
		\item Personalized citizen reporting channel and information broadcaster for rural areas. Users can send SMS, and receive follow-up messages periodically.
		\item Built core backend system using Django REST Framework and Twilio SMS Gateway API.
      \end{cvitems}
    }

  \cventry
    {Project Lead} % Empty position
    {Glucofood} % Project
    {Universitas Indonesia} % Empty location
    {May 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item Mobile Application SIG Ristek Fasilkom UI's external project.
		\item Personal daily nutrition tracking application, including calories, fat, and proteins, built using Flutter and Django REST Framework as its backend API.
		\item Led the whole development process, with the team consisting of 7 members.
      \end{cvitems}
    }
    
  \cventry
    {Mobile App Developer} % Empty position
    {Scrum Booster} % Project
    {Universitas Indonesia} % Empty location
    {February 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item Taken as a part of Software Engineering Project course, partnering with \textbf{Fasilkom UI's Reliable Software Engineering Lab} as its client.
		\item A "portable scrum handbook" application that helps Scrum methodology actors to boost their productivity and tackle their problems quickly by providing useful tips and insights 
		\item Worked with a team consisting of 6 members, built the app using Flutter.
      \end{cvitems}
    }
    
  \cventry
    {Database Designer, Backend Developer} % Empty position
    {Sistem Informasi Mahasiswa UI (SIMUI)} % Project
    {Universitas Indonesia} % Empty location
    {November 2018} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item Submission for Database course's Final Project assignment.
		\item A student information website that contains student's personal information, faculty and university's events list and its volunteer recruitment informations, along with recruitment platform. 
		\item Worked with a team consisting of 3 members, designed the database tables, schemes, triggers and stored procedures using PostgreSQL and developed the backend system using Django.
      \end{cvitems}
    }
    
  \cventry
    {Initiator} % Empty position
    {Foundations of Programming 0 (DDP 0)} % Project
    {Universitas Indonesia} % Empty location
    {June 2017} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
		\item An annual event held by students from 2nd year, to help newly accepted students in Fasilkom UI with no prior knowledge of programming to learn foundations of programming.
		\item Courses covered: Basic I/O, loops, functions, basic arithmetic computation.
		\item Initiated the event with the help of students from batch 2016.
      \end{cvitems}
    }
\end{cventries}